Reading Notes

### 2020-05-14 paper.tex
add a script to check if my bibfile is broken and added a bunch of new papers to start reading
started reading, will need to come back

>>>>

Of these the Alessandri paper was the best and  most interesting/relevant. I am pulling some refs from here for next time:

\cite{Mikhnenko2012}
Exciton diffusion length (EDL) in narrow bangap polymers. photoluminescense decay time is related and measurable. PCBM and PCDTBTs modeled with Monte Carlo--code available. They used P3HT as reference (5.4+/-0.7nm exciton diffusion length). 
Exciton diffusion is essential for organic solar cells. excitons are electron hole pairs created by excitation due to light absorption. they are separated into free charges at an interface which creates current. the movement of the excitons through hopping is what is refered to as diffusion. Exciton diffusion length is a factor in device efficiency.
Other methods to measure EDL are fluorescence quenching - the dependence of the exciton quenching efficiency vs semiconductor thickness is fit to 1D diffusion equation. Pros: direct measuremnt, cons: difficult experimentally and there are many things to consider in the model (FRET, effect of polymer-vaccuum interface, optical interference). 
This paper uses MC to model PL decay.
(Losing focus come back tomorrow)
\cite{Alessandri2017b}
\cite{Scharber2013}
\cite{Scharber2006a}
\cite{Yu1995}
\cite{Halls1995}
\cite{Kim2006}
\cite{Lee2011}
\cite{Huang2010}
\cite{Jankowski2013}
\cite{Marsh2014}
\cite{}
\cite{}
\cite{}
\cite{}
\cite{}
\cite{}
\cite{}
\cite{}
\cite{}
\cite{}
\cite{}
\cite{}
